
\noindent
\begin{tabular}{ll}
\textbf{Thesis} & LLM-based Wheel Human Interaction Robot for Receptionist and Human Assistant \\
\textbf{Student} & Mr. Kirawut Chalermkitpaisan, Mr. Krittin Sakharin, Ms. Natcha Rungruang, Ms Natwasa Manomaiwiboon \\
\textbf{Student ID.} & 65011333, 65011356, 65011386, 65011402 \\
\textbf{Degree} & Bachelor of Engineering \\
\textbf{Program} & Robotics and AI Engineering \\
\textbf{Year} & 2025 \\
\textbf{Thesis Advisor} & Asst. Prof. Dr. Sarucha Yanyong \\
%\textbf{Co-Thesis Advisor} & Assoc. Prof. Dr. Co-Thesis Advisor \\
\end{tabular}

\vspace{1cm}

\begin{center}
\textbf{\Large ABSTRACT IN ENGLISH}
\end{center}

\vspace{0cm}

This thesis presents the development and evaluation of Satu, a wheeled robotic assistant designed within the Robotics and Artificial Intelligence Engineering department  in Building E-12 at King Mongkut's Institute of Technology Ladkrabang. The primary objective of this project was to develop a robot capable of assisting with common tasks encountered in an academic building, including answering department-related questions in Thai and guiding users to specified locations, while remaining accessible and straightforward to interact with.

To handle conversational tasks, the system incorporates a large language model supported by a knowledge retrieval mechanism, which allows the robot to provide responses that are relevant and appropriate to the context of the department. Navigation is implemented using a ROS2-based framework, enabling the robot to move autonomously through the building by referencing a pre-constructed floor map. In addition to its functional capabilities, the physical design of the robot was developed with user experience in mind, aiming for an appearance that is welcoming and non-intimidating in order to encourage natural interaction. All of these components, which include speech processing, visual perception, navigation, and conversation handling, are brought together across multiple embedded computing devices to work as a single unified system.

The system was evaluated through multiple rounds of testing, in which performance across conversation understanding, navigation accuracy, and response appropriateness was measured. Results indicated consistent improvement between each round, with the final iteration satisfying all predefined performance criteria. The findings suggest that thoughtfully combining conversational artificial intelligence, mobile robotics, and human-centred design principles can produce a functional and reliable robotic assistant suitable for deployment in a real-world academic environment.