\chapter*{ACKNOWLEDGEMENT}
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENT}

We would like to express our sincere appreciation to Asst. Prof. Dr. Sarucha Yanyong, thesis advisor at the Department of Robotics and AI Engineering, School of Engineering, King Mongkut’s Institute of Technology Ladkrabang, for his guidance, insightful feedback, and continuous support throughout this project. His knowledge and dedication greatly influenced the direction and overall quality of this work.

We also extend our thanks to the professors, faculty members, and staff of the Department of Robotics and AI Engineering at KMITL for providing access to laboratory facilities, technical resources, and a supportive research environment. Their support in resolving technical challenges at various stages of the project is greatly appreciated.

In addition, we are grateful to our friends in the RAI program who participated in system testing and evaluation. Their interaction with the prototype, along with their valuable feedback, was essential in assessing the system’s performance and reliability under realistic conditions. Their guidance, encouragement, and collaboration throughout the project made this experience both productive and enjoyable.

Finally, we are deeply grateful to our families for their constant encouragement and understanding, which gave us the strength to persevere through challenges and complete this thesis.

\rightline{Kirawut Chalermkitpaisan, Krittin Sakharin,}
\rightline{Natcha Rungruang, and Natwasa Manomaiwiboon}