\chapter{LITERATURE REVIEW}

% =====================================================

\section{MECHANICAL DESIGN}

This section covers the mechanical aspects of the robotic assistant's design, including chassis, mobility systems, and structural components.
\subsection{Torque}
Torque is a measure of the rotational force applied to an object, calculated as the product of the force and the distance from the pivot point. In robotics, torque is crucial for determining the robot's ability to perform tasks that require rotation or movement against resistance. The required torque for a robotic joint can be calculated using the formula:

\begin{equation}
T = F x r
\label{eq:2.1}
\end{equation}

Where:
- \( T \) is the torque (in Newton-meters, Nm)
- \( F \) is the force applied (in Newtons, N)
- \( r \) is the distance from the pivot point to the point where the force is

\begin{itemize}
\item Torque Calculation for Robot Arm Motors
For robotic arms, torque is required to lift and manipulate objects. The torque needed is influenced by the mass of the object, the length of the arm, and gravitational force. The torque can be calculated using the formula:
    \begin{equation}
    T = m x g x l
    \label{eq:2.2}
    \end{equation}
    Where:
    - \( m \) is the mass of the object being lifted (in kilograms, kg)
    - \( g \) is the acceleration due to gravity (approximately 9.81 m/s²)
    - \( l \) is the length of the arm from the pivot point to the center (in meters, m)
If the arm consists of multiple segments, the total torque required is 
the sum of the torques from each segment: 
    \begin{equation}
    T_{total} = \sum_{i=1}^{n} (m_i x g x l_i)
    \label{eq:2.3}
    \end{equation}
    Where:
    
    - \( n \) is the number of segments in the arm

    - \( m_i \) is the mass of the object or segment at position \( i \)
    
    - \( l_i \) is the length from the pivot point to the center of mass of segment \( i \)

    - \(m_i\) and \(l_i\) correspond to the mass and length of each segment of the arm, including the object being manipulated. This calculation ensures that the motors selected for the robotic arm can provide sufficient torque to perform the desired tasks effectively.

\item Torque Calculation for Mobile Robot Wheels
For mobile robots, torque is required to overcome friction and move the robot. The torque needed can be calculated using the formula:
    \begin{equation}
    T = (M x a x F_r x F_i) x r
    \label{eq:2.4}
    \end{equation}
    Where:
    - \( M \) is the mass of the robot (in kilograms, kg)
    - \( a \) is the acceleration of the robot (in meters per second squared, m/s²)
    - \( F_r \) is the rolling resistance coefficient (dimensionless)
    - \( F_i \) is the incline factor (dimensionless, accounts for slope)
    - \( r \) is the radius of the wheel (in meters, m)
Since frictional losses and real-world conditions can impact performance, the actual motor torque should be selected with a safety margin, typically 1.5 to 2 times the calculated torque.
\end{itemize}

% -----------------------------------------------------------
\subsection{Kinematics}

% ===========================================================

\section{ELECTRICAL DESIGN}

This section covers the electrical systems, power management, and hardware integration aspects of the robot.
\subsection{Power Supply Architecture and Electrical Safety}
The power supply architecture of a mobile robotic system determines how electrical energy is arranged, distributed, and protected throughout the platform. In addition to supplying the required voltage and current to each subsystem, the electrical design must also ensure safe operation under normal and fault conditions. For this reason, both connection configuration and protection devices are important considerations in robotic electrical systems.

In electrical design, the arrangement of components can be classified into series and parallel connections. These two connection types have different electrical characteristics and are used for different purposes in robotic systems.

\subsubsection{Series and Parallel Connection}
A series connection is formed when components are connected in a single continuous path, causing the same current to flow through every element. In this arrangement, the total voltage across the circuit is equal to the sum of the voltage drops across each component to increase the voltage. The total voltage of a series-connected source can be expressed as:
\begin{equation}
    V_{total} = \sum_{i=1}^{n} (V_i)
\end{equation}
Where each \( V_i \) is the voltage of an individual component in the series.

A parallel connection provides multiple paths for current flow. In this arrangement, each branch receives the same supply voltage, while the total current is shared among the loads according to their individual requirements. The total current in a parallel circuit is given by:
\begin{equation}
    I_{total} = \sum_{i=1}^{n} (I_i)
\end{equation}
Where each \( I_i \) is the current drawn by an individual component in the parallel arrangement

\subsubsection{Electrical Safety Considerations}

Electrical safety considerations are important in robotic systems to prevent damage caused by reverse polarity, overcurrent, electrical transients, and hazardous operating conditions. Diodes are commonly used for reverse polarity protection and flyback suppression in inductive circuits. Circuit breakers are used to disconnect the power path when abnormal current is detected, protecting the system from overheating and electrical faults. In addition, an emergency stop (EMO) provides a manual method for immediately shutting down robot operation during unsafe situations. Proper wiring, grounding, and component selection further contribute to the safe and reliable operation of the robotic platform.

% ---------------------------------------------------------------------
\subsection{DC to DC Buck Converter}
A DC to DC buck converter is a type of switching voltage regulator used to reduce a higher direct current (DC) input voltage to a lower regulated DC output voltage. It is widely used in embedded systems, portable electronics, and mobile robotic platforms because many electronic components operate at voltage levels lower than the main battery supply. In robotic applications, a buck converter is especially important for powering low-voltage devices such as microcontrollers, sensors, single-board computers, and communication modules from a higher-voltage battery source.
The operation of a buck converter is based on the controlled switching of a semiconductor device, typically a transistor or MOSFET, together with an inductor, diode or synchronous switch, and output capacitor. When the switch is turned on, energy from the input source is transferred to the inductor and load. During this period, the inductor stores energy in its magnetic field. When the switch is turned off, the inductor releases its stored energy to the load through the freewheeling path, allowing the output current to continue flowing. The capacitor helps smooth the output voltage by reducing voltage ripple caused by the switching action. The output voltage of an ideal buck converter can be expressed as:

\begin{equation}
    V_{out} = D x V_{in}
\end{equation}
Where:
- \( V_{out} \) is the output voltage (in volts, V)

- \( D \) is the duty cycle (a value between 0 and 1)

- \( V_{in} \) is the input voltage (in volts, V)

In practical circuits, the output voltage is also influenced by component losses, switching frequency, load current, and internal resistance of the converter elements. Therefore, real buck converters are designed with feedback control mechanisms to maintain a stable output voltage even when the input voltage or load conditions vary. This voltage regulation characteristic is essential in robotic systems, where electronic modules may be sensitive to voltage fluctuations.

The efficiency of a converter is defined as the ratio of output power to input power, expressed as a percentage:

\begin{equation}
    \eta = \left( \frac{P_{out}}{P_{in}} \right) x 100\%
\end{equation}
Where:
- \( \eta \) is the efficiency of the converter (in percentage)

- \( P_{out} \) is the output power delivered to the load (in watts, W)

- \( P_{in} \) is the input power drawn from the source (in watts, W)

In summary, the DC to DC buck converter is a key component in modern robotic electrical systems because it provides efficient and regulated voltage conversion from the main battery supply to lower-voltage electronic subsystems. Its high efficiency, controllable output, and suitability for battery-powered applications make it an essential part of the electrical design of mobile robots.

% ---------------------------------------------------------------

\subsection{Power Consumption Analysis}

Power consumption is a fundamental consideration in the electrical design of mobile robotic systems because it directly affects operating time, system stability, component selection, and overall efficiency. A mobile robot typically consists of multiple electrical and electronic subsystems, such as embedded controllers, onboard computers, sensors, motor drivers, communication modules, and audio or display interfaces. Each subsystem consumes electrical power according to its voltage and current requirements. Therefore, understanding and estimating the total power demand of the robot is essential during the design stage.

In electrical systems, power is defined as the rate at which electrical energy is consumed by a load. The basic relationship between voltage, current, and power is expressed by:

\begin{equation}
    P = V x I
\end{equation}
Where:

- \( P \) is the power consumption (in watts, W)

- \( V \) is the voltage supplied to the component (in volts, V)

- \( I \) is the current drawn by the component (in amperes, A)

The total power consumption of a robotic platform can be expressed as the sum of the power consumed by all electrical loads:
\begin{equation}
    P_{total} = \sum_{i=1}^{n} (P_i)
\end{equation}
Where:
- \( P_i \) is the power consumption of each subsystem \( i \)

\begin{enumerate}
    \item Static Power Consumption: Static power consumption refers to the relatively constant power drawn by components that operate continuously, such as microcontrollers, onboard computers, LiDAR sensors, and communication modules.
    \item Dynamic Power Consumption: Dynamic power consumption refers to the variable power demand caused by components whose load changes during operation, particularly motors and actuators. For example, a robot may consume significantly more power while accelerating, turning, or carrying payloads than when it is idle or moving at constant speed.
\end{enumerate}

The operating time of a battery-powered robot can be roughly estimated using the battery energy capacity and the average system power consumption. Battery energy is commonly expressed in watt-hours (Wh), which can be calculated as:
\begin{equation}
    E = C x V
\end{equation}
Where:

- \( E \) is the energy capacity of the battery (in watt-hours, Wh)

- \( C \) is the battery capacity (in ampere-hours, Ah)

- \( V \) is the nominal voltage of the battery (in volts, V)

The estimated runtime of the robot can then be calculated as:
\begin{equation}
    T = \frac{E}{P_{total}}
\end{equation}
Where:
- \( T \) is the estimated runtime (in hours)
- \( P_{total} \) is the total power consumption of the robot (in watts)

In summary, power consumption is a key parameter in the design of mobile robotic systems. It influences battery selection, operating time, voltage regulation, thermal performance, and system reliability. A thorough understanding of voltage, current, and power relationships enables designers to estimate energy demand accurately and develop a stable electrical architecture suitable for continuous robotic operation.

% ---------------------------------------------------------------------------

\subsection{Electrical Interconnection and Power Distribution}

Electrical interconnection and power distribution are essential aspects of robotic electrical design because they determine how electrical energy is delivered from the power source to each subsystem in a safe, stable, and efficient manner. In a mobile robot, multiple components such as embedded controllers, onboard computers, sensors, motor drivers, audio modules, and communication devices operate simultaneously, often with different voltage and current requirements. Therefore, an appropriate electrical interconnection design is necessary to ensure that each subsystem receives the correct supply voltage and sufficient current for reliable operation.

Power distribution must also be designed to minimize undesirable effects such as voltage drop, electrical noise, and overheating. Voltage drop occurs when current flows through wires or connectors with finite resistance, reducing the effective voltage reaching the load. This can become significant in systems with long wires or high-current devices such as motors. To reduce voltage drop, designers typically use conductors with appropriate wire gauge, minimize unnecessary cable length, and ensure good-quality electrical connections. Stable voltage delivery is especially important for sensitive electronics such as microcontrollers, sensors, and onboard computers, which may malfunction if the supply voltage falls below their required operating range.

Electrical noise is another major concern in robotic systems, especially when low-power digital electronics and high-power actuators share the same power source. Motors, switching converters, and communication devices can introduce noise and transient disturbances into the power line. These disturbances may degrade sensor readings, interfere with communication signals, or affect processor stability. For this reason, electrical interconnection design often includes filtering capacitors, decoupling capacitors, proper grounding strategies, and physical separation between power and signal wiring. In some cases, sensitive subsystems are provided with isolated or separately regulated power lines to improve reliability. Thermal management is also a critical aspect of power distribution. High-current components such as motor drivers and voltage regulators can generate significant heat during operation. Proper heat dissipation through heatsinks, ventilation, or active cooling may be necessary to prevent overheating and ensure long-term reliability.

In addition, the power distribution architecture must consider the different operational characteristics of system components. High-current devices such as motors may produce sudden current surges during startup or direction changes, while computing units and sensors typically require stable, low-noise power supplies. Therefore, the electrical design should allocate power paths according to the characteristics of each load. Separating high-power and low-power branches can improve system stability and reduce interference between subsystems.

In summary, electrical interconnection and power distribution form the foundation of a reliable robotic electrical system. Proper distribution of power from the battery to all subsystems ensures that each component receives the required voltage and current while maintaining overall safety, stability, and efficiency.

% ===============================================================

\section{SOFTWARE DESIGN}

\subsection{Mobile Robot}

\subsubsection{ROS 2 (Robot Operating System 2)}

ROS 2 is an open-source robotic middleware framework that has become the de facto standard for robot software development. Designed from the ground up to overcome limitations of the original ROS, it provides comprehensive support for modern robotic systems, including multi-robot teams, resource-constrained embedded platforms, real-time control systems, and operation across unreliable networks. ROS 2 establishes well-defined design patterns and architectural conventions for structuring complex robotic software, supporting modularity, scalability, and maintainability in autonomous systems. It targets production-grade deployment environments where reliability and determinism are critical, combining distributed middleware capabilities with tools and libraries that streamline development of sophisticated control, perception, and communication subsystems. For this project, ROS 2 serves as the core integration middleware connecting all robot subsystems.

\subsubsection{ROS Navigation Stack}

The ROS Navigation Stack provides a comprehensive framework for autonomous mobile robot navigation, accepting odometry data and sensor stream inputs and outputting velocity commands to the robot's motor controller. This creates a clean abstraction that separates high-level path planning logic from low-level motor actuation. The Navigation Stack requires correct configuration of several components: ROS middleware access, a tf transform tree defining coordinate frame relationships between hardware components, standardised sensor data publication using ROS message types, and tuned costmap and planner parameters reflecting the robot's geometry and dynamics. This modular architecture enables robust navigation in diverse environments while supporting independent testing and development of individual components.

\subsubsection{AMCL (Adaptive Monte Carlo Localization)}

Adaptive Monte Carlo Localization (AMCL) is the primary localization package used within the ROS ecosystem for autonomous navigation tasks. The algorithm employs a particle filter approach, maintaining a probabilistic distribution of candidate robot poses and iteratively refining this distribution as new sensor observations and odometry measurements become available. AMCL is specifically optimised for use with 2D laser rangefinders and pre-built occupancy grid maps, making it well-suited to structured indoor environments.

It is important to note that AMCL is subject to specific operational constraints. The algorithm assumes a fixed geometric relationship between the laser sensor and the robot base; any movement of the laser relative to the base frame violates this assumption and can degrade localization accuracy significantly. Furthermore, AMCL requires continuous odometry input to propagate the particle filter over time. Odometry estimates may be derived from multiple complementary sensor sources, including wheel encoders and inertial measurement units (IMUs), which together provide more robust position and orientation estimates than either source alone.

\subsection{Database Management}

\subsubsection{Retrieval-Augmented Generation (RAG)}

Retrieval-Augmented Generation (RAG) is a technique that enhances large language model output quality by incorporating an external knowledge retrieval step before response generation. Rather than relying solely on patterns in the model's training parameters, RAG queries a domain-specific knowledge base at inference time, retrieving contextually relevant information to augment the model's context.

RAG offers cost-effective extension of LLM capabilities to specialised domains without expensive model retraining. By grounding responses in retrieved, current information, RAG substantially reduces factual hallucinations and improves relevance and accuracy. In this implementation, RAG forms the backbone of the knowledge retrieval subsystem, enabling contextually appropriate responses to user queries about the operating environment and domain-specific topics.

\subsubsection{Vector Database}

A vector database stores data as dense numerical vectors (embeddings) rather than conventional row-column structures, enabling similarity-based retrieval over large unstructured data collections including text, images, and audio. Vector databases support approximate nearest-neighbour search rather than exact-match queries, enabling retrieval of semantically related records even with differing query wording. This functionality is essential for RAG systems where semantic relevance rather than lexical overlap determines retrieval quality.

\subsubsection{Embeddings}

Embeddings are dense, fixed-dimensional numerical representations of objects — including text, images, and audio — produced by machine learning models trained to capture semantic and contextual relationships. Objects that are semantically similar are mapped to nearby points in the embedding space, enabling distance-based similarity measures to serve as a proxy for meaning. In this system, text embeddings represent both stored knowledge base documents and incoming user queries, enabling the vector database to identify and retrieve the most relevant passages for augmenting the LLM's response.

\subsubsection{Milvus}

Milvus is an open-source vector database platform specifically engineered for large-scale similarity search on massive embedding collections. Designed with production deployment in mind, Milvus provides highly optimised indexing structures and query algorithms that enable fast, accurate retrieval of semantically similar vectors from datasets containing millions or billions of embeddings. Unlike traditional relational databases, Milvus is purpose-built for vector search operations, supporting multiple similarity metrics including Euclidean distance, cosine similarity, and inner product.

Key features of Milvus include exceptional scalability through distributed architectures that allow horizontal expansion, high-performance approximate nearest-neighbour search capabilities that retrieve relevant results with minimal latency even on very large datasets, and flexible indexing strategies optimised for different trade-offs between search accuracy and computational efficiency. In this implementation, Milvus serves as the underlying vector database infrastructure for the RAG pipeline, enabling rapid semantic retrieval of domain-relevant information from the knowledge base to augment LLM responses.

\subsubsection{SQL (Structured Query Language)}

SQL is a standardised declarative programming language for defining, manipulating, and retrieving data in relational database management systems (RDBMS). Data is organised in tables with rows representing records and columns representing typed attributes. SQL provides comprehensive operations for schema creation, record insertion and updates, referential integrity enforcement, and complex multi-table queries through joins and aggregations. Query optimisation and index management facilities ensure retrieval performance at scale. In this system, SQL maintains structured records of user interactions, profiles, and system logs, complementing the vector database layer for semantic retrieval.

\subsection{Artificial Intelligence}

\subsubsection{Face Recognition}

Facial recognition is a biometric identification technology that authenticates or identifies individuals by analysing distinctive geometric and photometric features of the human face. It detects facial regions, generates compact feature representations, and compares them against stored facial templates. The system automatically identifies returning users and personalises interactions based on stored preferences and interaction history. This capability enhances human-robot interaction naturalness and continuity by eliminating explicit identification steps. For the robotic assistant, facial recognition enables context-aware, personalized engagement with individual users.

\subsubsection{Natural Language Processing (NLP)}

Natural Language Processing (NLP) is a multidisciplinary field enabling computational systems to understand, interpret, and generate human language in written and spoken forms. It combines rule-based linguistics, statistical models, and deep learning architectures for tasks including parsing, sentiment analysis, intent detection, and machine translation. NLP systems capture not only surface language form but also deeper semantic content, including speaker intent, implied meaning, and emotional tone. This nuanced understanding enables the robotic assistant to engage in natural, contextually appropriate dialogue, especially in open-domain settings with ambiguous or colloquial queries.

\subsubsection{Large Language Model (LLM)}

A Large Language Model (LLM) is a class of artificial intelligence system trained on massive corpora of text data — often comprising hundreds of billions of tokens — to acquire broad and deep competencies in understanding and generating human language. LLMs are built on the transformer neural network architecture, which leverages self-attention mechanisms to capture long-range dependencies between tokens and model the statistical structure of language at multiple levels of abstraction.

Through large-scale pre-training followed by task-specific fine-tuning or instruction alignment, LLMs develop the capacity to perform a diverse array of language tasks — including question answering, summarization, translation, and code generation — without requiring explicit task-specific training data for each application. In this system, the LLM serves as the central reasoning and response generation component of the conversational AI subsystem, processing retrieved contextual information from the RAG pipeline to produce coherent, factually grounded responses to user queries.

\subsubsection{Text-to-Speech (TTS)}

Text-to-Speech (TTS) is a speech synthesis technology that converts written text into natural-sounding spoken audio, enabling AI systems to communicate verbally with users without requiring pre-recorded audio assets. Modern TTS systems are built on deep learning architectures — including neural vocoders and sequence-to-sequence models — that generate speech with dynamic, context-sensitive variations in prosody, pitch, speaking rate, and pronunciation. These characteristics produce output that closely approximates natural human speech patterns, significantly improving comprehensibility and user engagement compared with earlier rule-based synthesis methods.

TTS technology has found widespread application in accessibility tools for visually impaired users, virtual assistants, and interactive voice response systems. For the robotic assistant, TTS serves as the primary output modality for verbal communication, enabling the robot to deliver responses audibly in environments where visual screen interaction is impractical or undesirable.

\subsubsection{Automatic Speech Recognition (ASR)}

Automatic Speech Recognition (ASR) is a technology that processes raw acoustic speech signals and converts them into machine-readable text, forming the primary input pathway for voice-driven human-machine interaction. Contemporary ASR systems employ end-to-end deep learning architectures — including recurrent neural networks and transformer-based models — trained on large-scale speech corpora to achieve high transcription accuracy across a range of speakers, accents, and acoustic conditions.

Advanced ASR implementations integrate Natural Language Processing modules downstream of the transcription stage, enabling the system to infer the user's intent and semantic meaning from the recognised text in addition to producing a verbatim transcript. ASR accuracy is sensitive to several environmental factors, including background noise levels, microphone quality, and speaker proximity; consequently, robust noise handling and signal preprocessing are important design considerations for deployment in real-world robotic environments. Despite these challenges, modern ASR systems are capable of achieving near real-time transcription latency, enabling fluid conversational interactions between the user and the robotic assistant.